Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-18 paper/paper.tex
pass on classification

Accessing attachments was engineering-wise simpler compared to
embedded tests. For that, we wrote a crawler to visit the issue
trackers of all four engines listed in Table~\ref{tab:engines} and we
were able to retrieve a total of 627 files (\jsc{}=147, \veight{}=370,
and \smonkey{}=110).

To mine tests from the textual descriptions we proceeded as
follows. First, we broke the text describing the issue in paragraphs
and used a binary classifier to label each paragraph as ``code'' or
``not code''. Then, based on that information, we merged consecutive
paragraphs labeled as ``code'' and used a \js\ parser to check
well-formedness of the corresponding code fragment. Using that method
we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
find a public classifier to solve the problem above. For space, we
summarize the solution that worked the best in the following. The
classifier that performed best for this case uses
a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
  what this ``Embeddings'' thing does at a high-level. Also, if this
  stuff exists why we did not find a solution off-the-shelf?} that
builds on a neural net~\Fix{cite} to keep a dictionary of words and the
similarity distance among them\Mar{but we are talking about
  sentences. how does it go from words to sentences? Note that many
  words from the ``code'' vocabulary are from English!}. In more
detail, the classification model uses a Convolutional Neural
Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
  meaning for each layer?} and has been trained and evaluated using a
dataset with 25K samples of English paragraphs and 25K snippets of
\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
evaluate the model and obtained a predicted accuracy of
\Fix{98\%}. This classifier is publicly available from our website as
a separate component.

>>>>

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\Fix{627} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\Fix{XX} files. All those files were included in
Table~\ref{tab:test-suites}. For the classification of ``code''
vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
NLP technique to produce word embeddings. A word embedding is a
mapping of words---in our case, sentences---to vectors of real
numbers. With that mapping it is possible to measure distance between
two sentences as the distance between the vectors characterizing
them. Consequently, one can measure, for example, the minimum distance
between a sentence in English and a sentence in a \js\ embedding,
built with word2vec using a corpus of \js\ sentences. \Mar{Please
  confirm if this is the idea! If yes, shouldn't just one corpus
  (e.g., the JS corpus) be enough to solve the problem? Are there two
  separate embeddings (one for English and one for JS)? If not, how
  they are combined? What about the classification scheme?  It needs
  to answer yes/no (not a distance).}  We used a corpus with 25K
samples of English paragraphs and 25K snippets of \js{} code and
obtained a classifier with accuracy of 98\%. This classifier is
publicly available from our website as a separate component.

%% For space, we summarize the solution that worked the best in
%% the following. The classifier that performed best for this case uses a
%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
%%   exists why we did not find a solution off-the-shelf?}  that builds
%% on a neural net~\Fix{cite} to keep a dictionary of words and the
%% similarity distance among them\Mar{but we are talking about
%%   sentences. how does it go from words to sentences? Note that many
%%   words from the ``code'' vocabulary are from English!}. In more
%% detail, the classification model uses a Convolutional Neural
%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
%%   meaning for each layer?} and has been trained and evaluated using a
%% dataset with 25K samples of English paragraphs and 25K snippets of
%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
%% evaluate the model and obtained a predicted accuracy of
%% \Fix{98\%}. This classifier is publicly available from our website as
%% a separate component.
